SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on Disks

### 2015-07-19 papers/B1555_EdgeOn/B1555_letter.tex
update of current 2-SIE parameters
draft update & model dat files

It was first suggested by \citet{Mao1998} that flux-ratio anomalies
observed in radio-loud multiple images of lensed quasars could be
interpreted as a telltale sign of the presence of substructure in lens
galaxies.  Indeed, small perturbations in the gravitational potential
are sufficient to cause flux-ratio anomalies in strong lensed systems
\citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
radio band, lensed images are neither sensitive to microlensing from
stars, nor to dust extinction. This makes flux-ratio anomalies a promising
tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002,N13} [NEED MORE REF].  
At present, the amount of substructure derived from flux-ratio anomalies
seems to be disagreement with predictions from numerical simulations, with
the former requiring a larger fraction of mass in substructure than
expected \citep{Xu14}. While this could be the result of small sample
statistics, it could also be an indication that flux-ratio anomalies
have a different origin than substructure.[COMMENT ON LINE OF SIGHT EFFECTS?--LEON]
%
An alternative method for
the detection of substructure in gravitational lens galaxies, utilizing
the surface brightness distribution of extended arcs and Einstein rings
has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a,V12}, \textbf{although the number of detections remains small}.

@@

To model B1555+375, we use the lens modelling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image
positions and flux densities measured by the radio observations.
\textbf{We use the image positions from \citet{Marlow99}, who also presented a singular isothermal ellipsoid
(SIE) model that provided a good fit to the image positions but
does not reproduce the strong flux-ratio anomaly between components A
and B.}  %\citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow99}.  
\textbf{The flux measurements are performed by \citet{K03} with a half year monitoring to obtain flux-ratio curves, providing throughout discussions in erros on flux densities.}

Although the flux-ratio anomaly that is observed in the radio data \textbf{implies there must be some perturbation to the mass model, which} may be
caused by substructure in the lensing galaxy, our high-resolution near
infrared imaging suggests another explanation.  In both the $K^\prime$
band adaptive optics data and the \textit{HST} infrared imaging (\textbf{see} in
Fig. 1), the lensing galaxy has a clear edge-on disk component with a
position angle of $\approx 10$ degree.  We therefore model the system
with a disk component in order to see if such a model can explain the
flux-ratio anomaly without the need for substructure.  The edge-on
disk may also explain the system morphology that is observed in the
near infrared imaging.  In particular, neither image B nor image D is
detected in the Keck AO data (Fig.~\ref{fig:merlin}), and both of
these lensed images lie on or close to the edge-on disk.  Thus, strong
extinction in the disk could cause the \textbf{non-}detection of these
images.[REF B0128 PAPER?--LEON]

As a first trial of modelling, we create a single SIE model to check
the performance of a simple lensing potential. Consistent with
previous studies \citep{Marlow99, Xu14}, a single elliptical
potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.
[WHY MODEL BULGE W/ SIE? COMMENT ON THE REASON FOR PICKING MODELS--LEON]
[I TRY TO EXPLAIN HERE AND MAY NEED TO BE MORE FOCUS--JW]
\textbf{We notice that the lensed images are close to the center of B1555+375 since its edge-on disk spreads further out of the Einstein radius in the \textit{HST} imaging. Instead of constructing the lens galaxy with a primary NFW halo, a secondary bulge, plus an elongated disk, we consider only the bulge plus an disk component, reducing the number of free parameters in the model. Also with only four lensed images, mass profiles that are too complicated will not be informative in the lens modelling.}
We then create two separate models of the lensing potential that both
incorporate the disk.  In the first we treat the lens as a SIE bulge\textbf{/halo}
and an exponential edge-on disk (SIE+expdisk). In the second model
the disk is represented as a very elongated SIE component (2-SIE). 
The lens system is red, with a strong jump in flux between the F814W
(roughly I) and F160W (roughly H) bands (Fig.~\ref{fig:multiband}), so
we assign a lens redshift of $z_\ell = 1.0$ and a source redshift of
$z_s =1.5$. \textbf{This assumption on redshifts is needed because some lens model parameters contain distance information. However, our choice of redshifts does not affect the predicted magnifications nor flux-ratios.}

\textbf{For each model, we explore the parameter space in the following way: 
(1) Preparation of model starting point: Applying the information in the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the edge-on disk component. We then use the best-fit model of \citet{Marlow99} as the starting point for the bulge\textbf{/halo} component and also the source position. The rest of parameters in the disk component are set to be the same as the bulge/halo component as the starting point.
(2) First optimization: Bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec, and run optimization with amoeba algorithm in {\tt glafic} to reach a first optimal model.
(3) Markov Chain Monte Carlo: Use the parameters from optimal result as the starting point. We then run MCMC in {\tt glafic} to obtain the best-fit parameters.} 
%The smallest $\chi^2$ doesn't necessarily give a physical model. Here are the examples we would like to discard: the ellipticity and the position angle of the disk component are far from what we see in the SHARP AO image, the center positions of two components are too far apart physically, or the positions of the lenses and the source are clearly located outside the Einstein radius in the image.
%(3) Optimize for physical lens models: We bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec and then run optimization with amoeba algorithm to reach the final best-fit for each model.}

The \textbf{final} best-fit parameters are shown in Table
2. Both of these models produce lensed images with positions and
fluxes that are good matches to the radio observations.  While both of
the two component models produce significantly improved matches to the
fluxes than the single SIE model, the 2-SIE version has a somewhat
better performance than the SIE+expdisk model in reproducing flux
ratios. The comparison of the observations and our lens modelling is
given in Figure 3 and Tables 3 \& 4.  We have not included an external
shear component into our model because the constraints provided by the
image positions and fluxes would not be sufficient to constrain such a
model. However, we note that the image not affected by dust (image C)
in the Keck AO data is consistent with negligible shear (i.e. shear
strength $\Gamma_s=0.002$), when modeled with the pixelized technique
of \citet{V09}.

@@

\begin{figure}
%\plotone{point_source.eps}
\includegraphics[width=84mm]{point_source.eps}
\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375. The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model [NOT UPDETED YET], marked by a black filled circle. \label{fig2}}
\end{figure}

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 lens models. Subscripts 1 and 2 represent bulge\textbf{/halo} and disk components in each model respectively. Positions are offsets from radio image component A measured in units of arcsec. The velocity dispersion $\sigma$ is in units of $km/s$ and disk mass $M_{tot}$ is in units of $h^{-1} M_{\odot}$. \textbf{$e$ is ellipticity defined as the axis ratio $q=1-e$ }and $\theta$ is the position angle measured east of north.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & \multicolumn{2}{c}{Lens model} \\
		&SIE+expdisk& 2-SIE		   
\\
\hline
$x_1$  	  & $-0.1794$	& $-0.1884$  \\
$y_1$	  &$-0.1881$	&$-0.1607$  \\

$\sigma_1$ &$140.3$     & $145.3$ \\
$e_1$	  & $0.21$	& $0.24$ \\
$\theta_1$ &$73.6 \degr$ & $99.5 \degr$ \\
\hline
$x_2$	  &$-0.1639$ 	&$-0.1594$  \\
$y_2$	  &$-0.2542$	& $-0.2225$  \\
$M_{tot,2}$  & $3.58\times 10^{10} $  & ...	 \\  
$\sigma_2$ & ...        &$122.7$ \\  
$e_2$	  &$0.84$	&$0.82$  \\
$\theta_2$ &$4.0\degr$ &$6.5\degr$  \\
$r_e$	  & $0.21 ''$ &  ... \\
\hline
%$\chi ^2$ & $1.05$ & $0.04$ \\
%\hline
\end{tabular}

%\end{minipage}

\end{table}

\begin{table*}
%\centering
 \begin{minipage}{140mm}
  \caption{Radio observation \citep{Marlow99} and model-predicted lensed image positions (in arcsec). Both SIE+expdisk and 2-SIE lens model-predicted positions well match to the radio observation.}
  \begin{tabular}{@{}ccccccc}

\hline

Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{4}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} &\multicolumn{2}{c}{ 2-SIE}		\\
					 &East &North &East 		&North &East 		&North\\ 
\hline
A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
B ........ &$-0.0726(0.001)$ 	&$+0.0480(0.001)$	&$-0.0723$ &$+0.0480$ & $-0.0726 $  &  $+0.0480$  \\  
C ........ &$-0.4117(0.001)$  &$-0.0280(0.001)$	&$-0.4114$ &$-0.0282$  & $-0.4117 $  &   $-0.0280$ \\  
D ........ &$-0.1619(0.006)$  &$-0.3680(0.006)$	&$-0.1631$ &$-0.3628$  & $-0.1619$    &  $-0.3680$ \\  
\hline
\end{tabular}

\end{minipage}
\medskip

\end{table*}

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Comparison between radio data \citep{K03} and model-predicted flux-ratios.}
  \begin{tabular}{@{}ccccccc}

\hline
	& MERLIN  & \multicolumn{3}{c}{Model}\\
		&5 GHz   & 1-SIE & SIE+expdisk & 2-SIE\\
\hline
$f_A/f_B$			&$1.61 (0.10)$ &$1.04$& $1.62$ & $1.61$ \\ 
$f_A/f_C$		&$1.97 (0.12)$ 	 &$3.20$ & $2.89$ & $1.97$\\
$f_A/f_D$		&$11.62 (3.24)$  &$9.67$& $9.30$ & $11.63$\\

@@

%\end{minipage}
\medskip

\end{table}

>>>>

It was first suggested by \citet{Mao1998} that flux-ratio anomalies
observed in radio-loud multiple images of lensed quasars could be
interpreted as a telltale sign of the presence of substructure in lens
galaxies.  Indeed, small perturbations in the gravitational potential
are sufficient to cause flux-ratio anomalies in strong lensed systems
\citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
radio band, lensed images are neither sensitive to microlensing from
stars, nor to dust extinction. This makes flux-ratio anomalies a promising
tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002,K05,V09,N13}.  
At present, the amount of substructure derived from flux-ratio anomalies
seems to be disagreement with predictions from numerical simulations, with
the former requiring a larger fraction of mass in substructure than
expected \citep{Xu14}. While this could be the result of small sample
statistics, it could also be an indication that flux-ratio anomalies
have a different origin than substructure.[COMMENT ON LINE OF SIGHT EFFECTS?--LEON]
%
An alternative method for
the detection of substructure in gravitational lens galaxies, utilizing
the surface brightness distribution of extended arcs and Einstein rings
has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a,V12}, \textbf{although the number of detections remains small}.

@@

%To model B1555+375, we use the lens modelling code {\tt glafic} \citep{Oguri}.  
\textbf{To model B1555+375, we use the lens modelling code {\tt gravlens} \citep{Kee01}.  
The inputs to the model are the observed image
positions and flux densities measured by the radio observations.
We use the image positions from \citet{Marlow99}, who also presented a singular isothermal ellipsoid
(SIE) model that provided a good fit to the image positions but
does not reproduce the strong flux-ratio anomaly between components A
and B.}  %\citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow99}.  
\textbf{The flux measurements are performed by \citet{K03} with a half year monitoring to obtain flux-ratio curves, providing throughout discussions in erros on flux densities.}

Although the flux-ratio anomaly that is observed in the radio data implies there must be some perturbations to the mass model, which may be
caused by substructure in the lensing galaxy, our high-resolution near
infrared imaging suggests another explanation.  In both the $K^\prime$
band adaptive optics data and the \textit{HST} infrared imaging (see in
Fig. 1), the lensing galaxy has a clear edge-on disk component with a
position angle of $\approx 10$ degree.  We therefore model the system
with a disk component in order to see if such a model can explain the
flux-ratio anomaly without the need for substructure.  The edge-on
disk may also explain the system morphology that is observed in the
near infrared imaging.  In particular, neither image B nor image D is
detected in the Keck AO data (Fig.~\ref{fig:merlin}), and both of
these lensed images lie on or close to the edge-on disk.  Thus, strong
extinction in the disk could cause the non-detection of these
images.[REF B0128 PAPER?--LEON]

As a first trial of modelling, we create a single SIE model to check
the performance of a simple lensing potential. Consistent with
previous studies \citep{Marlow99, Xu14}, a single elliptical
potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.
\textbf{Our next step is to examine the idea that if an edge-on disk can cause similar perturbations to the lens like substructures which resulting in flux ratio anomalies in merging images. In \citet{Kee98}, they explore strong lensing by spiral glaxies with SIE+ exponential disk+NFW model, corresponding to the bulge, disk, and halo respectively. An exponential disk profile best describes the disk component in spiral galaxies because it matches the light distribution of disk. We thus choose a SIE plus exponential disk model (SIE+expdisk) in our study of B1555+375, focusing on the role of an edge-on disk passing through the merging double in the lens system. }
%We then create two separate models of the lensing potential that both
%incorporate the disk.  In the first we treat the lens as a SIE bulge\textbf{/halo}
%and an exponential edge-on disk (SIE+expdisk). In the second model
%the disk is represented as a very elongated SIE component (2-SIE). 
The lens system is red, with a strong jump in flux between the F814W
(roughly I) and F160W (roughly H) bands (Fig.~\ref{fig:multiband}), so
we assign a lens redshift of $z_\ell = 1.0$ and a source redshift of
$z_s =1.5$. \textbf{This assumption on redshifts is needed because some lens model parameters contain distance information. However, our choice of redshifts does not affect the predicted magnifications nor flux-ratios.}

\textbf{To obtain the optimal lens model, we explore the parameter space in the following way: 
(1) Preparation of model starting point: Applying the priori infromation from the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the exponential disk. We then use the best-fit model of \citet{Marlow99} as the starting point for the SIE profile and also the source position. The rest of parameters of exponential disk are set to be the same as the SIE component as the starting point.
(2) Optimal model search: We let all model parameter varies but bind the centroid position of two conponents with a strong Gaussian prior ($\sigma = 0.05 $ arcsec). Run optimization with amoeba algorithm in {\tt gravlens} interatively to reach the global minimum of $chi^2$ in paramter space.
(3) Markov Chain Monte Carlo: After obtaining the optimal lens model, we run MCMC to explore the parameter space for the model uncertainties.} 
%The smallest $\chi^2$ doesn't necessarily give a physical model. Here are the examples we would like to discard: the ellipticity and the position angle of the disk component are far from what we see in the SHARP AO image, the center positions of two components are too far apart physically, or the positions of the lenses and the source are clearly located outside the Einstein radius in the image.
%(3) Optimize for physical lens models: We bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec and then run optimization with amoeba algorithm to reach the final best-fit for each model.}

The best-fit parameters are shown in Table 2. 
%Both of these models produce lensed images with positions and
%fluxes that are good matches to the radio observations.  
%While both of the two component models 
\textbf{By adding an elongated exponential disk to a smooth potential model,  our lens model shows significant improvement on the flux ratios when comparing to the single SIE model, includeing the flux ratio anomaly between the merging images.}
%the 2-SIE version has a somewhat
%better performance than the SIE+expdisk model in reproducing flux
%ratios. 
The comparison of the observations and our lens modelling is
given in Figure 3 and Tables 3 \& 4.  We have not included a third component such as an external
shear component or NFW halo into our model because the number of constraints provided by the
image positions and fluxes would not be sufficient to constrain such a
model. However, we note that the image not affected by dust (image C)
in the Keck AO data is consistent with negligible shear (i.e. shear
strength $\Gamma_s=0.002$), when modeled with the pixelized technique
of \citet{V09}.

@@

\begin{figure}
%\plotone{point_source.eps}
\includegraphics[width=84mm]{gravlens_exp_try5_plot.eps}
\caption{Radio observation(blue plus sign) and model-predicted(red open circle) image positions of B1555+375. Criticle curves are shown with blue solid line and caustics are shown with red dash line. The position of the source is at $(-0.1953,-0.1494)$, marked by a red filled circle. The centroid positions of two lens components are marked by black filled triangles.  \label{fig2}}
\end{figure}

%\begin{figure}
%\plotone{point_source.eps}
%\includegraphics[width=84mm]{point_source.eps}
%\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375. The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model [NOT UPDETED YET], marked by a black filled circle. \label{fig2}}
%\end{figure}

\begin{table}
 \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 lens model. Positions are offsets from radio image component A measured in units of arcsec. The velocity dispersion $\sigma$ is in units of $km/s$. \textbf{$e$ is ellipticity defined as the axis ratio $q=1-e$ }and $\theta$ is the position angle measured east of north.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & SIE & Expdisk 		   
\\
\hline
$x$  	  & $-0.1818$	&$-0.1472$ 	  \\
$y$	  &$-0.1988$	&$-0.2057$	 \\

$b$ &$0.21 $  & ...   \\
$\kappa_0$ & ... & $0.11$        \\  
$e$	  & $0.31$	&$0.87$ \\
$\theta$ &$2.96 \degr$ &$7.0\degr$ \\
$r_s$	& ...  & $0.28$\\
\hline
%$\chi ^2$ & $1.05$ & $0.04$ \\
%\hline
\end{tabular}

%\end{minipage}
\end{table}

%\begin{table}

%  \caption{Best-fit parameters of B1555+375 lens models. Subscripts 1 and 2 represent bulge\textbf{/halo} and disk components in each model respectively. Positions are offsets from radio image component A measured in units of arcsec. The velocity dispersion $\sigma$ is in units of $km/s$ and disk mass $M_{tot}$ is in units of $h^{-1} M_{\odot}$. \textbf{$e$ is ellipticity defined as the axis ratio $q=1-e$ }and $\theta$ is the position angle measured east of north.}
%  \begin{tabular}{@{}ccc}
%\hline 
% Parameter  & \multicolumn{2}{c}{Lens model} \\
%		&SIE+expdisk& 2-SIE		   
%\\
%\hline
%$x_1$  	  & $-0.1794$	& $-0.1771$  \\
%$y_1$	  &$-0.1881$	&$-0.2032$  \\

%$\sigma_1$ &$140.3$     & $146.1$ \\
%$e_1$	  & $0.21$	& $0.15$ \\
%$\theta_1$ &$73.6 \degr$ & $155.3 \degr$ \\
%\hline
%$x_2$	  &$-0.1639$ 	&$-0.1562$  \\
%$y_2$	  &$-0.2542$	& $-0.2195$  \\
%$M_{tot,2}$  & $3.58\times 10^{10} $  & ...	 \\  
%$\sigma_2$ & ...        &$122.6$ \\  
%$e_2$	  &$0.84$	&$0.86$  \\
%$\theta_2$ &$4.0\degr$ &$7.9\degr$  \\
%$r_e$	  & $0.21 ''$ &  ... \\
%\hline
%$\chi ^2$ & $1.05$ & $0.04$ \\
%\hline
%\end{tabular}
%\end{table}

\begin{table*}
\centering
 \begin{minipage}{140mm}
  \caption{Radio observation \citep{Marlow99} and model-predicted lensed image positions (in arcsec).}
  \begin{tabular}{@{}ccccccc}
\hline

Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{2}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} 	\\
					 &East &North &East 		&North \\ 
\hline
A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
B ........ &$-0.0726(0.001)$ 	&$+0.0480(0.001)$	&$-0.0727$ &$+0.0477$  \\  
C ........ &$-0.4117(0.001)$  &$-0.0280(0.001)$	&$-0.4117$ &$-0.0281$   \\  
D ........ &$-0.1619(0.006)$  &$-0.3680(0.006)$	&$-0.1630$ &$-0.3653$  \\  
\hline
\end{tabular}

\end{minipage}
\medskip
\end{table*}

%\begin{table*}
%\centering
 %\begin{minipage}{140mm}
 % \caption{Radio observation \citep{Marlow99} and model-predicted lensed image positions (in arcsec). Both SIE+expdisk and 2-SIE lens model-predicted positions well match to the radio observation.}
 % \begin{tabular}{@{}ccccccc}

%\hline

%Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{4}{c}{Model} \\
%					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} &\multicolumn{2}{c}{ 2-SIE}		\\
%					 &East &North &East 		&North &East 		&North\\ 
%\hline
%A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
%B ........ &$-0.0726(0.001)$ 	&$+0.0480(0.001)$	&$-0.0723$ &$+0.0480$ & $-0.0755 $  &  $+0.0414$  \\  
%C ........ &$-0.4117(0.001)$  &$-0.0280(0.001)$	&$-0.4114$ &$-0.0282$  & $-0.4122 $  &   $-0.0267$ \\  
%D ........ &$-0.1619(0.006)$  &$-0.3680(0.006)$	&$-0.1631$ &$-0.3628$  & $-0.1620$    &  $-0.3533$ \\  
%\hline
%\end{tabular}

%\end{minipage}
%medskip
%\end{table*}

\begin{table}
 \centering
% \begin{minipage}{140mm}
  \caption{Comparison between radio data \citep{K03} and model-predicted flux-ratios.}
  \begin{tabular}{@{}ccccccc}

\hline
	& MERLIN  & \multicolumn{2}{c}{Model}\\
		&5 GHz   & 1-SIE & SIE+expdisk \\
\hline
$f_A/f_B$			&$1.61 (0.10)$ &$1.04$& $1.62$  \\ 
$f_A/f_C$		&$1.97 (0.12)$ 	 &$3.20$ & $2.17$ \\
$f_A/f_D$		&$11.62 (3.24)$  &$9.67$& $8.69$ \\

@@

%\end{minipage}
\medskip
\end{table}

%\begin{table}
% \centering
% \begin{minipage}{140mm}
%  \caption{Comparison between radio data \citep{K03} and model-predicted flux-ratios.}
% \begin{tabular}{@{}ccccccc}

%\hline
%	& MERLIN  & \multicolumn{3}{c}{Model}\\
%		&5 GHz   & 1-SIE & SIE+expdisk & 2-SIE\\
%\hline
%$f_A/f_B$			&$1.61 (0.10)$ &$1.04$& $1.62$ & $1.62$ \\ 
%$f_A/f_C$		&$1.97 (0.12)$ 	 &$3.20$ & $2.89$ & $2.00$\\
%$f_A/f_D$		&$11.62 (3.24)$  &$9.67$& $9.30$ & $11.56$\\

%\hline
%\end{tabular}

%\end{minipage}
%\medskip
%\end{table}
